---
title: "Colors Of Thrones"
author: "Jeena Lee"
date: "May 20, 2016"
output: html_document
---

This is a work in progress. These are the color schemes I have created so far. Feedback is welcome.

```{r, echo=FALSE}
library(ggplot2)
library(gridExtra)
# Creating dummy data for plotting.
duck_ht <- rnorm(100, mean=20, sd=4)
beav_ht <- rnorm(100, mean=15, sd=3)
dwarf_ht <- rnorm(100, mean=27, sd=3)
dog_ht <- rnorm(100, mean=25, sd=5)
cat_ht <- rnorm(100, mean=22, sd=3/5)
species <- c(rep("duck", 100), rep("beav", 100), rep("dwarf", 100), rep("dog", 100), rep("cat", 100))
heights <- c(duck_ht, beav_ht, dwarf_ht, dog_ht, cat_ht)
five_data <- data.frame(heights, species)
heights <- heights[1:400]
species <- species[1:400]
four_data <- data.frame(heights, species)

# Creating functions for plotting data.
jitter_4plot <- function(c, ...) {
  ggplot(four_data, aes(species, heights, color=species)) +
    geom_jitter(position=position_jitter(width=0.1)) +
    scale_color_manual(values=c)
}

jitter_5plot <- function(c, ...) {
  ggplot(five_data, aes(species, heights, color=species)) +
    geom_jitter(position=position_jitter(width=0.1)) +
    scale_color_manual(values=c)
}

multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

print_palette <- function(x, ...) {
  par(pin=c(2,4))
  n <- length(x)
  old <- par(mar = c(5, 0.5, 5, 0.5))
  on.exit(par(old))
  
  image(1:n, 1, as.matrix(1:n), col=x,
        ylab="", xaxt="n", yaxt="n", bty="n", xlab="")
}

dot_graph <- function(c, ...) {
  ggplot(iris, aes(Sepal.Length, Petal.Width, color=Species)) +
  geom_point(size=3) +
  scale_color_manual(values=c)
}

volcano_graph <- function(c, ...) {
  image(volcano, col=colorRampPalette(c)(50))
}
```


```{r, echo=FALSE}
# The color schemes.
Lannister <- c("#8A0A03", "#D49E00", "#611D3A", "#423939")
Greyjoy <- c("#20427D", "#458D9C", "#007666", "#133952", "#576769") 
Targeryan <- c("#467D64", "#72627F", "#BFB479", "#976466", "#6E6144")
Martell <- c("#E6B10B", "#CC6300", "#A60B00", "#651A00")
Arryn <- c("#156679","#36AAC6", "#88E8FF", "#79695A", "#C6B4A4")
Arryn2 <- c("#21BCD1", "#A3E5F5", "#006185", "#D2C0B2", "#AC7A72")
Tyrell <- c("#0A6B3A", "#EBBD13", "#A62B40", "#78AB29", "#C47340")
Tyrell2 <- c("#73B270", "#FFF0B5", "#DEF2B4", "#B26B73")
Baratheon <- c("#2A4C2E", "#EBC52C", "#453A30", "#A6574A", "#8FAB39")
Tully <- c("#899E9C", "#3288B0", "#EB736B", "#DEC066")
```

##Lannister: crimson, gold, wine, armor-grey
```{r, echo=FALSE}
print_palette(Lannister)
volcano_graph(Lannister)
multiplot(jitter_4plot(Lannister), dot_graph(Lannister), cols=2)
```

##Greyjoy: Cold ocean at night
```{r, echo=FALSE}
print_palette(Greyjoy)
volcano_graph(Greyjoy)
multiplot(jitter_5plot(Greyjoy), dot_graph(Greyjoy), cols=2)
```

##Targeryan: Dragon eggs, and dragon-y colors
```{r, echo=FALSE}
print_palette(Targeryan)
volcano_graph(Targeryan)
multiplot(jitter_5plot(Targeryan), dot_graph(Targeryan), cols=2)
```

##Martell: SUN!
```{r, echo=FALSE}
print_palette(Martell)
volcano_graph(Martell)
multiplot(jitter_4plot(Martell), dot_graph(Martell), cols=2)
```

##Arryn: Day sky
```{r, echo=FALSE}
print_palette(Arryn)
volcano_graph(Arryn)
multiplot(jitter_5plot(Arryn), dot_graph(Arryn), cols=2)
```

##Tyrell: Primal colors of fields and golden roses
```{r, echo=FALSE}
print_palette(Tyrell)
volcano_graph(Tyrell)
multiplot(jitter_5plot(Tyrell), dot_graph(Tyrell), cols=2)
```

##Tyrell2: Muted colors of fields and golden roses
```{r, echo=FALSE}
print_palette(Tyrell2)
volcano_graph(Tyrell2)
multiplot(jitter_4plot(Tyrell2), dot_graph(Tyrell2), cols=2)
```

##Baratheon: Hunting in the fields
```{r, echo=FALSE}
print_palette(Baratheon)
volcano_graph(Baratheon)
multiplot(jitter_5plot(Baratheon), dot_graph(Baratheon, cols=2))
```

##Tully: Silver trout leaping in the river
```{r, echo=FALSE}
print_palette(Tully)
volcano_graph(Tully)
multiplot(jitter_4plot(Tully), dot_graph(Tully), cols=2)
```
